%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same
% directory as this .tex file. These files provide the resume style and themes
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[11pt,a4paper,roman]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{classic} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage[utf8]{inputenc}
%\usepackage[T1, T2A]{fontenc}
%\usepackage[serbian]{babel}
\usepackage{indentfirst}
%\setlength{\parindent}{1.5cm}

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template
\usepackage{multicol}

\usepackage[scale=0.85]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Andrija} % Your first name
\familyname{Petrovic} % Your last name

% All information in this block is optional, comment out any lines you don't need
\title{Cover Letter}
\address{Center for Business Decision Making\\Faculty of Organizational Sciences\\ University of Belgrade}{Jove Ilica 154}{11000 Belgrade, Serbia}
\mobile{(+381) 066~8896~051}
%\phone{(000) 111 1112}
%\fax{(000) 111 1113}
\email{aapetrovic@mas.bg.ac.rs}
%\homepage{www.linkedin.com} % The first argument is the url for the clickable link, the second argument is the url displayed in the template - this allows special characters to be displayed such as the tilde in this example
%\extrainfo{Born 18.06.1985.}


%----------------------------------------------------------------------------------------

\begin{document}

%\makecvtitle % Print the CV title



%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

\clearpage

\recipient{Editor-in-Chief}{Expert Systems with Applications} % Letter recipient

%\recipient{HR Departmnet}{Austcorp\\Sidney\\Australia} % Letter recipient
\date{\today} % Letter date
\opening{Dear Editor,} % Opening greeting
\closing{Sincerely,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

\makelettertitle % Print letter title


Please find enclosed our manuscript, “Structured Prediction of Sparse Dependent Variables for Traffic State Etimation in Large-Scale Networks ” by Andrija Petrovi\'c, Sandro Radovanovi\'c, Mladen Nikoli\'c, Boris Delibasi\'c, and Milo\v s Jovanovi\'c, which we would like to submit for publication in Expert Systems with Applications.


In this manuscript we propose a hybrid of two Gaussian Conditional Random Field models (one recently proposed for classification, and one for regression) for inference of traffic speed, a relevant variable for traffic state estimation and travel information systems. It addresses two specifics of the problem -- sparsity in traffic data and the fact that observations are not independent. The proposed model showed better prediction performance compared to several unstructured and structured models.
Our contribution is twofold. Firstly, we contribute to the state-of-art in data mining by proposing a new hybrid approach for prediction of dependent sparse variables. Secondly, we contribute to the state-of-art in traffic state estimation by proposing two traffic state estimation models of two large-scale real-world networks.

In order to comply with article policy, as a corresponding author on behalf of all the authors I would like to confirm that the manuscript has not been published elsewhere, accepted for publication elsewhere or under editorial review for publication elsewhere; and that my Institute's (University of Belgrade) representative is fully aware of this submission. Additionally, I confirm that instructions for authors of this journal have been read carefully and that the manuscript complies to all points.


Thank you for your consideration.

\vspace{10mm}

\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document} 